### 2020-03-08 Common/chapters/transfer_learning.tex
Julien and Johan: new model split figure

\subsubsection{Manual transfer learning}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Cl{\'e}ment}}The second Python script allows to perform each transfer learning step by hand. Thanks to this, a good combination of hyperparameters can be searched for without having to run the whole pipeline. The command line arguments slighty differ from the automated version. Table \ref{table:manual_transfer_learning_options} lists them. First of all, a single training set and a single validation set have to be specificied. In addition to this, a second dataset is required: the reference/target one, which does not change throughout the process. This dataset is useful for the global performance graphs (see Section \ref{sec:global_performance}). Another parameter used for the global performance graphs is the '-{}-last{\_}layer'. Its role is limited to this, unless '-{}-{}attach{\_}DM' is set to True. In this case, the decision maker loaded as '-{}-last{\_}layer' is attached to the current model, provided the current step is a frozen one. This option is used at the last frozen step (target dataset), as this decision maker comes from the first training (target dataset as well)	. Doing this instead of a using a new random decision maker (as it is the case for the non-target datasets) allows to start with a skilled decision maker and optimize it according to the features learned during the transfer learning.

@@

\textbf{-{}-training-set1}     & Path to training set 1                                                                                                                                                                                                  & True                                                                        & String        \\ \hline
\textbf{-{}-validation-set1}   & Path to validation set 1                                                                                                                                                                                                                                                                                                                                                                                                  & True                                                                        & String        \\ \hline
\textbf{-{}-test-set1}     & Path to test set 1                                                                                                                                                                                                                                                                                                                                                                                                   & True                                                                        & String        \\ \hline
\textbf{-{}-training-set2}     & Path to training set 2                                                                                                                                                                                                 & True                                                                        & String        \\ \hline
\textbf{-{}-validation-set2}   & Path to validation set 2 

@@

\textbf{-{}-training-set3}     & Path to training set 3                                                                                                                                                                                                  & True                                                                        & String        \\ \hline
\textbf{-{}-validation-set3}   & Path to validation set 3                                                                                                                                                                                                                                                                                                                                                                                                  & True                                                                        & String        \\ \hline

@@

\textbf{-{}-cuda-device}      & \begin{tabular}[c]{@{}l@{}}GPU name to run the experiment\\For example: 'cuda:0', 'cuda:1', ...\end{tabular}                                                                                                                                                                                      & \begin{tabular}[c]{@{}l@{}}False\\ Default: 'cuda'\end{tabular}             & String        \\ \hline

@@

\textbf{-{}-optimized-metric} & \begin{tabular}[c]{@{}l@{}}Metric to optimize\\ The best model during the training will be saved according to it\\{[}'auc', 'accuracy', 'precision', 'recall', 'f1score', 'specificity'{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}False\\ Default: 'auc'\end{tabular}              & String        \\ \hline

>>>>

\subsubsection{Manual transfer learning}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Cl{\'e}ment}}The second Python script allows to perform each transfer learning step by hand. Thanks to this, a good combination of hyperparameters can be searched for without having to run the whole pipeline. The command line arguments slighty differ from the automated version. Table \ref{table:manual_transfer_learning_options} lists them. First of all, a single training set and a single validation set have to be specificied. In addition to this, a second dataset is required: the reference/target one, which does not change throughout the process. This dataset is useful for the global performance graphs (see Section \ref{sec:global_performance}). Another parameter used for the global performance graphs is the '-{}-last{\_}layer'. Its role is limited to this, unless '-{}-{}attach{\_}DM' is set to True. In this case, the decision maker loaded as '-{}-last{\_}layer' is attached to the current model, provided the current step is a frozen one. This option is used at the last frozen step (target dataset), as this decision maker comes from the first training (target dataset as well). Doing this instead of a using a new random decision maker (as it is the case for the non-target datasets) allows to start with a skilled decision maker and optimize it according to the features learned during the transfer learning.

@@

\textbf{-{}-trainingset1}     & Path to training set 1                                                                                                                                                                                                  & True                                                                        & String        \\ \hline
\textbf{-{}-validationset1}   & Path to validation set 1                                                                                                                                                                                                                                                                                                                                                                                                  & True                                                                        & String        \\ \hline
\textbf{-{}-testset1}     & Path to test set 1                                                                                                                                                                                                                                                                                                                                                                                                   & True                                                                        & String        \\ \hline
\textbf{-{}-trainingset2}     & Path to training set 2                                                                                                                                                                                                 & True                                                                        & String        \\ \hline
\textbf{-{}-validationset2}   & Path to validation set 2 

@@

\textbf{-{}-trainingset3}     & Path to training set 3                                                                                                                                                                                                  & True                                                                        & String        \\ \hline
\textbf{-{}-validationset3}   & Path to validation set 3                                                                                                                                                                                                                                                                                                                                                                                                  & True                                                                        & String        \\ \hline

@@

@@
